Improving Haskell Theory Exploration

### 2015-11-24 TransferReport/report.tex
More TODOs
Added future
Remove examples for now

\begin{abstract}
Theory Exploration is a promising approach to improving the quality and understanding of software, above that available through testing, in languages which are amenable to formal analysis such as those based on pure functional programming. Current techniques are limited by their computational cost, which we mitigate through a divide and conquer approach: reducing the problem size whilst using a machine learning approach to preserve relevant details.
\end{abstract}

\input{intro.tex}
\input{background.tex}
\input{contributions.tex}
\input{implementation.tex}

\iffalse
\section{First Results}

TODO

Future work?
Hypothetical use cases?
\fi

\input{related.tex}

\section{Future Work}
\label{future}

\iffalse
TODO

interestingness
\fi

\section{Conclusion}
\label{conclusion}

>>>>

\begin{abstract}
Theory Exploration is a promising approach to improving the quality and understanding of software, above that available through testing, in languages which are amenable to formal analysis such as those based on pure functional programming. Current theory exploration techniques are limited by their use of exponential time algorithms, which we mitigate by intelligently reducing the size of large inputs, using machine learning to preserve the relationships needed for successful exploration.
\end{abstract}

\input{intro.tex}
\input{background.tex}
\input{contributions.tex}
\input{implementation.tex}
\input{related.tex}
\input{evaluation.tex}
\input{future.tex}
\iffalse TODO: Section that brings back ML discussion to TE is missing \fi
